The Set Covering Problem (SCP), a well-known combinatorial optimization problem [2], is a classical problem in computer science that belongs o the class of NP-complete problems. It involves selecting the from a group of set of subsets, the subsets that include (cover) all the elements of the main set. The set covering problem has applications, both in real-life and theoretical research from resource allocation in manufacturing to personnel schedule management or finding the smallest set of labels to display that covers every item in a labelled database.   The set cover problem can also come in weighted or unweighted form.  In the weighted form, there is a notion of cost attached to each selected subset, i.e., selecting a subset has a different implication from selecting another. In this case, the objective is, usually, to both cover the main set and achieve optimal results in terms of the cost. This is often referred to as the Minimum Set Cover Problem (MSCP)
Background
The Set Covering Problem is one of most studied optimization problems in the field of mathematical programming \cite{yelbay2012set}. Several algorithms have been proposed for this problem from finding optimal solutions through exhaustive searches to heuristic approximation methods \cite{gomes2006experimental}. Gomes et al. in \cite{gomes2006experimental} , conducted an experimental analysis of the approximation algorithms to evaluate the merits and demerits of the approximation approaches, and how they operate. Their work revealed a performance gap between what is theoretically possible in literature and the results of the experimental evaluation. Many approximations algorithms have been proposed afterwards and more experiments to achieve better performances \cite{akhter2015heuristic}. Till date, more approximation techniques are still being proposed in literature to get more and more closer to optimal performances reported in literature. This work is also one of such as it proposes three, easy to implement algorithms for the MSCP. In the rest of this work, we will be presenting the formal definition of the problem, the approaches proposed in the work and experimental evaluation of the approaches. 
